Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach

### 2016-06-03 abstract.tex
Reduce the seismicity part and remove the earthquakes.
first draft sent to english review

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method. In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.  The aftershocks and foreshocks are removed from the catalog and the magnitude time series are generated for each tectonic seismic zone. Using declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e. $< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining  the results of this study with two similar previous studies, improves the linear correlation coefficient factor and empower the idea of universal relationship between $b-value$ and $k-M$ slope. The behavior of  the VG's properties are similar to previous studies and could be considered an alternative method for analyzing the earthquake sequence. 
\end{abstract}

>>>>

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method. In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh. Using declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e. $< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining  the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$ and empower the idea of universal relationship between $b-value$ and $k-M$ slope. The behavior of  the VG's properties are similar to previous studies and could be considered as an alternative method for analyzing earthquake sequences. 
\end{abstract}

### 2016-06-03 conclusion.tex
second draft of paper.
first draft sent to english review

\section{Conclusion}
We studied the earthquake sequence of three tectonic seismic regions of north Iran. Results manifest the strong relationship between $k-M$ slope and Gutenberg-Richter parameters. The variation of $k-M$ slope and $b-value$ with time in sliding windows have similar behavior and drops down before big earthquakes. Significant reduction of $<T_C>$ value before big earthquake is observed. Higher coefficient of variation of $k-M$ slope in comparison with $b-value$'s CV, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$. In general, $k-M$ and $b-value$ relationship preserves the behavior with variation of the window size and threshold magnitude, and could be an alternative approach for clustering the earthquake sequences based on different tectonic seismic zones.

>>>>

\section{Conclusion}
\noindent
We studied the earthquake sequence of three tectonic seismic regions of north Iran. Results manifest the strong relationship between $k-M$ slope and Gutenberg-Richter parameters. The variation of $k-M$ slope and $b-value$ with time in sliding windows have similar behavior and drops down before big earthquakes. Significant reduction of $<T_C>$ value before big earthquake is observed. Higher coefficient of variation of $k-M$ slope in comparison with $b-value$, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$. In general, $k-M$ and $b-value$ relationship preserves the behavior with variation of the window size and threshold magnitude, and could be an alternative approach for clustering the earthquake sequences based on different tectonic seismic zones.

### 2016-06-03 introduction.tex
first draft sent to english review

\begin{equation}
\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} 
\end{equation}

\noindent
where, $y$ is the value and $t$ is the time of the event. $k$ is the index of any event occurring between event $i$ and event $j$. The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at the right and left side (if there is any) of the event  (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}. This concept has applications ranging in various fields including geophysical studies.

\noindent
The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series. \citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method. Applying different threshold magnitude and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and independent of the threshold magnitude. In another research, \citet{Telesca2013} studied the Seismicity of the Mexican subduction zone through visibility graph approach. They extracted the characteristics of the visibility graph for five different tectonic seismic regions.  According to their study visibility graph could identify one of the regions that has a different seismicity characteristics, which is because of different tectonic processes that governs the area. The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line of Magnitude  of each event $(M)$ and its connectivity degree $(k)$) is investigated in their study. In a similar article \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph. They classified seismic catalog into shallow and deep earthquakes and extract the visibility graph characteristics for each class. According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph. High linear correlation coefficient value (close to 1)of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  \citet{Telesca2016} , used the $ <T_C>$, as the parameter window mean interval connectivity time ,  that indicates the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequences in the Kachchh region of western India. They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog. Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks. \\

\noindent
In this study we used visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran. The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region. \\

>>>>

\begin{equation}
\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
\end{equation}

\noindent
where, $y$ is the value and $t$ is the time of the event. $k$ is the index of any event occurring between event $i$ and event $j$. The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  and 3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}. This concept has applications ranging in various fields including geophysical studies.

\noindent
The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series. \citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method. Applying different threshold magnitudes and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and to be independent of the threshold magnitude. In another research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through visibility graph approach. They extracted characteristics of the visibility graph for five different tectonic seismic regions.  According to their study, visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes that governs the area. The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line fitting the Magnitude  of each event $(M)$ and its connectivity degree $(k)$) was investigated in their study. In a similar article, \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph. They classified seismic catalog into shallow and deep earthquakes and extracted the visibility graph characteristics for each class. According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph. High linear correlation coefficient value (close to 1) of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  \citet{Telesca2016} , defined the $ <T_C>$, as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequence in the Kachchh region of western India. They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog. Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks. \\

\noindent
In this study we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region \citep{Nemati2015} . \\

### 2016-06-03 main.tex
Added shima's comments.
first draft sent to english review

% Document Settings
\documentclass[a4paper,review]{elsarticle}

@@

% Long Title
\title{Visibility Graph Analysis of the 2005-2015 Earthquake Sequence in Northern Iran}

% Authors
%\author[label1]{Naeem Khoshnevis\corref{cor1}}
%\author[label1,label2]{Shima AzizzadehRoodpish}
%\cortext[cor1]{Corresponding author. Tel: \\
 %                    Email address: nkhshnvs@memphis.edu (N.Khoshnevis)}

@@

\begin{keyword}
Visibility Graph \sep Earthquake Magnitude \sep North Iran \sep b-value

>>>>

% Document Settings

% review
%\documentclass[authoryear,preprint,review,12pt]{elsarticle}

% final
% \documentclass[final,1p,times,authoryear]{elsarticle}

\documentclass[authoryear,preprint,review,12pt]{elsarticle}

@@

% Long Title
\title{Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach}

% Authors
\author[label1]{Naeem Khoshnevis\corref{cor1}}
%\author[label1,label2]{Shima AzizzadehRoodpish}
\cortext[cor1]{Corresponding author. Tel: \\
                  Email address: nkhshnvs@memphis.edu (N.Khoshnevis)}

@@

\begin{keyword}
Visibility Graph \sep Earthquake sequence \sep Magnitude \sep North Iran \sep b-value

### 2016-06-03 results.tex
first draft sent to english review

\begin{table}[h]
\centering
\caption{Seismic parameters and K-M slope values for north Iran tectonic seismic zones.}
\begin{tabular}{ccccc}
Region          & Number of Earthquake &  Mc &  b-value & K-M slope \\ \hline
Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
Alborz            & 488                               & 2.9   & 0.8532  & 9.2821      \\ \hline
Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
\end{tabular}
\label{tab:b_k_m_param}
\end{table}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
\caption{ K-M relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
\label{fig:k_m_plot_m}
\end{figure}

@@

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}}  
\end{equation}

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions. \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the size of the whole catalog. For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations $(std/mean)$}
\label{fig:random}
\end{figure}

 \noindent
The $k-M$ slope shows higher coefficient of variation. We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.

 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. Adding the results of the current study into the results of two previous similar studies improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:regression}
\end{figure}

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows. The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window. There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

\noindent
\citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area. The decreasing of the $<Tc>$ for large earthquakes have been shown in the figure. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude. The fluctuation of magnitude time series' topology properties (e.g. the $k-M$ slope and $<Tc>$) could be affected by the window size. Sharp changes in the VG parameters happens through small windows. Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}. %In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:tc}
\end{figure}

>>>>

\begin{table}[h]
\centering
\caption{Seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
\begin{tabular}{ccccc}
Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
\end{tabular}
\label{tab:b_k_m_param}
\end{table}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
\label{fig:k_m_plot_m}
\end{figure}

@@

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
\end{equation}

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions. \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively) and the maximum size is the size of the whole catalog. For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
\label{fig:random}
\end{figure}

 \noindent
The coefficient of variation of parameters are shown in Fig.~\ref{fig:random}. The $k-M$ slope shows higher coefficient of variation. We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.

 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and north Iran)}
\label{fig:regression}
\end{figure}

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows. The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window. There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $k-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

\noindent
\citet{Telesca2016} observed the decreasing in $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area and decrease in $<Tc>$ befor large earthquakes is clearly visible. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude. Fig.~\ref{fig:tc} shows the decrement of value of $< T_C >$, $k-M$, and $b-value$ before big earthquakes.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) with time. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake.}
\label{fig:tc}
\end{figure}

### 2016-06-03 seismicity.tex
first draft sent to english review

\section{Tectonic seismic regions and seismicity parameters}
\noindent
Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes. These earthquakes are categorized in various tectonic seismic zones. Based on seismicity parameters different tectonic seismic devisions have been defined for Iran.  Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}. \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.  Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions. \\

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
\caption{a) Map of Iran and surrounding countries. The study area is situated in the gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities indicated with circles. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

@@

\subsection{Magnitude Conversion}
\noindent
The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scale (reference). We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}. There are also some of data recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.

@@

\subsection{Catalog Completeness}
\noindent
Completeness of catalog is an important factor in studying the earthquake sequence.  In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000}. According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for picking the completeness magnitude for each catalog include: 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process. For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.  \citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% as a threshold to select completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.

@@

\noindent
In this study we assumed the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.9, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for the three regions. Earthquakes with magnitude bigger than completeness magnitude are represented.

>>>>

\section{Tectonic seismic regions and seismicity parameters}
\noindent
Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes. Based on seismicity parameters, different tectonic seismic devisions have been defined for Iran.  Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}. \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of the northern Iran.  Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions. \\

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
\caption{a) Map of Iran and surrounding countries. The study area is situated in the gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented, and location of big cities indicated with circles. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

@@

\subsection{Magnitude Conversion}
\noindent
The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scales \citep{IIEES}. We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}. There are also some of data recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.

@@

\subsection{Catalog Completeness}
\noindent
Completeness of catalog is an important factor in studying the earthquake sequence.  In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000} to determine the completeness magnitude. According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for picking the completeness magnitude for each catalog include: 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value somehow the cumulative number of events obey the power law distribution, and 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process in order to calculate the goodness of fit for each magnitude. \citet{Wiemer2000} assumed the goodness of fit of 90\% as a threshold to select completeness of the catalog. However,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} , shows the goodness of fit values for three tectonic seismic regions. For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit or the first magnitude with goodness of fit bigger than 90\%.

@@

\noindent
In this study we assume the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for the three regions. Earthquakes with magnitude bigger than completeness magnitude are represented.
